%% ------------------------------------------------------------------------
%% A template to produce a nice-looking cover letter.
%% ------------------------------------------------------------------------

\documentclass[11pt]{letter}

%% ------------------------------------------------------------------------
%% Metadata
%% ------------------------------------------------------------------------

\def\name{Eric Fritz}
\def\address{\href{http://www4.uwm.edu/ceas/cs/}{CEAS Department} \\ 3400 N. Cramer, \\ \vspace{-0.05in} Milwaukee, \textsc{wi} 53201}

\def\contactname{Contact Name}
\def\contactaddress{Senior Staff Recruiter \\ XYZ Corporation \\ City, State 12345}

\signature{\name}

%% ------------------------------------------------------------------------
%% Required style files
%% ------------------------------------------------------------------------

\usepackage{url}

% page margins
\usepackage[left=1.5in,top=1in,right=1.5in,bottom=1in,nohead]{geometry}

% hyperlink color
\usepackage[usenames,dvipsnames]{color}

% hyperlinks
\usepackage[colorlinks=true,urlcolor=BlueViolet,plainpages=false,]{hyperref}

%% ------------------------------------------------------------------------
%% Document
%% ------------------------------------------------------------------------

\begin{document}

\begin{letter}{\contactname \\ \contactaddress}

\begin{center}
	{\large\bf Eric Fritz} \\ 
	\href{http://www4.uwm.edu/ceas/cs/}{CEAS Department} \\ 3400 N. Cramer, \\ \vspace{-0.05in} Milwaukee, \textsc{wi} 53201
\end{center} \vfill

\opening{Dear \contactname,}

\noindent State what specific position you are applying for or inquiring about and how you learned of the opportunity.  Then, determine the flow of the rest of the letter, i.e. "This internship opportunity aligns with my career goals and would capitalize on my design skills."

\noindent Address any areas you may have referred to in your first paragraph (education, experience, career interests, etc).  Most students discuss the degree they are pursuing and where they are pursuing it.  You will also want to highlight how you meet their qualifications with a specific example of your background.  

\noindent Thank them for their time and consideration.  Let them know the best way to reach you and list both your e-mail and phone number.  Suggest an action plan, request an interview, let them know of and when you will be following up.  Remember to include your resume.  

\closing{Sincerely,}
\encl{Resume}

\end{letter}
\end{document}
