%% ------------------------------------------------------------------------
%% A template to produce a nice-looking resume.
%%
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%% Copyright 2011-2012 Eric Fritz (eric@eric-fritz.com).
%%
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License version 1.3c,
%% available at http://www.latex-project.org/lppl/.
%% ------------------------------------------------------------------------

\documentclass[10pt,a4paper,nolmodern]{moderncv}

\usepackage{eric-fritz}

%% ------------------------------------------------------------------------
%% Resume
%% ------------------------------------------------------------------------

\begin{document}

\maketitle

%%
%% Introduction
%%

Programmer who is passionate about software seeks a position as a developer, overcoming challenging problems with creative solutions.

%%
%% Skills
%%

\section{Skills}

\subsection{Extremely Proficient With}
\cvcomputer{Languages}{PHP, C\#, Java, Python, SQL, JavaScript}
           {OS}{Windows, Ubuntu \& Debian, OSX}
\cvcomputer{Databases}{MySQL, MsSQL, SQLite}
           {Web}{HTML, CSS, jQuery, AJAX}
\cvcomputer{Frameworks}{ASP.NET MVC3, Symfony2}
           {Tools}{Visual Studio, Eclipse, Git, Subversion}

\subsection{Have Experience With}
\cvcomputer{Languages}{C, C++, VB.NET, Scala, Ruby, Haskell}
           {Tools}{\LaTeX{}, Apache, Mercurial}
\cvcomputer{Databases}{Redis, MongoDB, CouchDB, FlockDB}
           {}{}

%%
%% Education
%%

\section{Education}

%% MS Computer Science

\cventry{2001-present}{MS, Computer Science}{University of Wisconsin - Milwaukee}{Milwaukee, WI}{}{
GPA: 4.0/4.0\\
Relevant Coursework:
}

\cvlistdoubleitem{Discrete Mathematics}{Algorithm Design \& Analysis}
\cvlistdoubleitem{Computer Architecture}{Operating Systems}

%% BFA Film

\cventry{2007-2011}{BFA, Film - Minor, Computer Science}{University of Wisconsin - Milwaukee}{Milwaukee, WI}{}{
GPA: 3.593/4.0\\
Honors: Cum Laude, Dean's Honor List, Senior Honors\\
Relevant Coursework:
}

\cvlistdoubleitem{Data Structures}{Assembly and Machine Language Programming}
\cvlistdoubleitem{Programming Language Concepts}{}

%%
%% Career History
%%

\section{Experience}

\subsection{Career History}

%% ESDN, Inc.

\cventry{2008-2009, 2011}{Software Developer}{ESDN, Inc.}{Janesville, WI}{}{
Developed and maintained a customizable e-commerce platform for hundreds of jewelry retailers and brands.
Maintained constant communication with designers, testers, and database developers to ensure quality work.
Designed and implemented an application that managed `collections' of jewelry products between brands.
Redesigned and implemented a locations management application which provided highly-demanded features and a better UX than its predecessor.
Implemented an e-marketing system for jewelry retailers.  
}

\cvline{}{Technologies used: C\#, Java, SQL (MySQL and MsSQL), ASP.NET MVC3, LINQ to SQL, HTML, CSS, Javascript, jQuery, Subversion\medskip}

%% ZoomShift, Inc.

\cventry{2011}{Freelance Software Developer}{EMM Holdings, LLC.}{Milwaukee, WI}{}{
Worked with an accelerated startup.
Implemented an administrative panel for organization and employee management.
Conversion of raw PHP templates into hierarchal and reusable components using the Twig template engine.
Preparatory work for migrating raw SQL queries into a separate model layer using the Doctrine2 SQL ORM.
}

\cvline{}{Technologies used: PHP, SQL (MySQL), \href{http://twig.sensiolabs.org/}{Twig}, \href{http://www.doctrine-project.org/}{Doctrine2}, HTML, CSS, Javascript, jQuery, Git\medskip}

%%
%% Teaching Experience
%%

\subsection{Teaching History}

\cventry{2011-2012}{Teaching Assistant}{University of Wisconsin-Milwaukee}{Milwaukee, WI}{}{
Prepared and presented new programming concepts and techniques.
Conducted two laboratory sections for for {\href{http://www.cs.uwm.edu/classes/cs201/semester/index.html}{CS201 - Computer Programming}} per semester.
Evaluated and maintained grades for student homework, quizzes, and exams.
}

\end{document}
